---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Marq Schieber"
date: "2/27/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

What are the dimensions of the Denny’s dataset? (Hint: Use inline R code and functions like nrow and ncol to compose your answer.) What does each row in the dataset represent? What are the variables?

Dimensions: 1643 rwos by 6 collumns. The variables include: address, city, latitude, longitude, state and zip. Each row is a different Denny's location.



```{r}
nrow(dennys)
ncol(dennys)
ls(dennys)
```


### Exercise 2

What are the dimensions of the La Quinta’s dataset? What does each row in the dataset represent? What are the variables?

Dimensions: 909 by 6
Rows: La Quinta Locations
Variables: address, city, latitude, longitude, state and zip

```{r}
nrow(laquinta)
ncol(laquinta)
ls(laquinta)
```


### Exercise 3

Take a look at the websites that the data come from (linked above). Are there any La Quinta’s locations outside of the US? If so, which countries? What about Denny’s?

No Denny's are found abroad.

La Quinta can be found outside the US in: Canada, Mexico, China, New Zealand, Honduras, Turkey, UAE, Chile and Colombia.

...

### Exercise 4

Brainstorming: You could filter by state. Any non-US states are abroad. 




### Exercise 5

  
```{r}
dennys %>%
  filter(!(state %in% states$abbreviation))
```
  
  0 locations

### Exercise 6

```{r}
dennys %>%
  mutate(country = "United States")
```

### Exercise 7

```{r}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```

### Exercise 8

```{r}
laquinta %>%
  mutate(country = case_when(
    state %in% states$abbreviation ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "FM" ~"Honduras",
    state %in% c("AG" , "QR" , "CH" , "NL" , "VE" , "PU" , "SL") ~ "Mexico"
  )) %>%
  filter(country == "United States")
```

### Exercise 9


Add exercise headings as needed.

